---
title: 'NLP Deliverable'
author: 'Ana Marin Estañ'
output: html_notebook
---

# **Madrid's airbnb reviews, sentiment analysis**

&nbsp;

&nbsp;

## 1. Check prerequesites

* Check if all needed packages are installed and added to the library
* Set work directory


```{r}
options(warn=-1)

packages <- c('rstudioapi', 
              'DT', 
              'tm',
              'ggplot2',
              'textcat',
              'wordcloud',
              'RWeka',
              'reshape2', 
              'tidyverse', 
              'tidytext', 
              'stringr',
              'dplyr', 
              'topicmodels')

install.packages(setdiff(packages, rownames(installed.packages())))  
rm(packages)

library(rstudioapi)
library(DT)
library(tm)
library(ggplot2)
library(textcat)
library(wordcloud)
library(RWeka)
library(reshape2)
library(tidyverse)
library(tidytext)
library(stringr)
library(dplyr)
library(topicmodels)
```

```{r}
setwd(dirname(getActiveDocumentContext()$path ))
cat('Working directory:', getwd())
```

&nbsp;

## 2. Import data and basic exploration

* Import review data form data folder
* Explore number of reviews and features
* Display basic data table

```{r}
reviews <- read_csv('data/reviews.csv')
cat('Number of reviews:', nrow(reviews), '\nColumn names:', names(reviews))
```

```{r}
datatable(head(reviews, 10))
```

&nbsp;

## 3. Basic data preprocessing 

* Limit data to 2500 random reviews 
* Detect review language
* Group reviews by language and show 10 most frequent languages
* Keep reviews written in English and Spanish (two most frequent languages) in two different data frames
* Remove empty reviews

```{r}
reviewsPrep = reviews[sample(nrow(reviews), 2500),]

reviewsPrep$language <- textcat(reviewsPrep$comments)
reviewsPrep$language <- as.factor(reviewsPrep$language)

languageCount = count(reviewsPrep, language)
languageCount = languageCount[order(languageCount$n, decreasing = T),]
languageCount$percentage <- (languageCount$n/2000)*100
languageCount[1:10,]

reviewsEn = reviewsPrep[c(reviewsPrep$language == 'english'),]
reviewsEs = reviewsPrep[c(reviewsPrep$language == 'spanish'),]

reviewsEn = reviewsEn[!(is.na(reviewsEn$comments) | reviewsEn$comments==''), ]
reviewsEs = reviewsEs[!(is.na(reviewsEs$comments) | reviewsEs$comments==''), ]
```

&nbsp;

## 4. Corpora creation, inspection and transformations 

Two different corpora are created: one containing English reviews, and other with the Spanish ones.
First, these corpora are inspected:

* Check length
* Summary of 5 first entries
* Meta and content of first entry

Each of this corpora is preprocessed:

* Limit number of entries to 1000
* Transform to lower case
* Remove numbers, Stopwords and punctuation
* Stemming
* Strip white spaces

Finally, the first document of each corpus is compared before and after being preprocessed

### English
```{r}
# Creation and inspection
corpusEn = VCorpus(VectorSource(reviewsEn$comments))
cat('English corpus length:', length(corpusEn), 'entries')

summary(corpusEn[1:5]); meta(corpusEn[[1]]); content(corpusEn[[1]])

# Transformation
if(length(corpusEn) > 1000) {
  corpusEn=corpusEn[1:1000]
  cat('Limit English corpus length to:', length(corpusEn), 'entries')
  }
stopwordsEn = c(stopwords(),'airbnb', 'madrid','stay')
corpusEnT <- tm_map(corpusEn, content_transformer(tolower))
corpusEnT <- tm_map(corpusEnT, content_transformer(removeNumbers))
corpusEnT <- tm_map(corpusEnT, content_transformer(removeWords), stopwordsEn)
corpusEnT <- tm_map(corpusEnT, content_transformer(removePunctuation))
corpusEnT <- tm_map(corpusEnT, content_transformer(stemDocument))
corpusEnT <- tm_map(corpusEnT, content_transformer(stripWhitespace))
```

Original and transformed reviews
```{r}
corpusEn[['100']][['content']]
corpusEnT[['100']][['content']]
```

### Spanish
```{r}
# Creation and inspection
corpusEs = VCorpus(VectorSource(reviewsEs$comments))
cat('Spanish corpus length:', length(corpusEs), 'entries')
summary(corpusEs[1:5]); meta(corpusEs[[1]]); content(corpusEs[[1]])

# Transformation
if(length(corpusEs) > 1000) {
  corpusEs=corpusEs[1:1000]
  cat('Limit Spanish corpus length to:', length(corpusEs), 'entries')
  }
  
stopwordsEs = c(stopwords('spanish'), 'madrid', 'airbnb')
corpusEsT <- tm_map(corpusEs, content_transformer(tolower))
corpusEsT <- tm_map(corpusEsT, content_transformer(removeNumbers))
corpusEsT <- tm_map(corpusEsT, content_transformer(removeWords), stopwordsEs)
corpusEsT <- tm_map(corpusEsT, content_transformer(removePunctuation))
corpusEsT <- tm_map(corpusEsT, content_transformer(stemDocument))
corpusEsT <- tm_map(corpusEsT, content_transformer(stripWhitespace))
```

Original and transformed reviews
```{r}
corpusEs[['50']][['content']]
corpusEsT[['50']][['content']]
```

&nbsp;

## 5. Create TDM

In this section Term-Document matrixes are created with TF-IDF weighting

```{r}
tdmEn = TermDocumentMatrix(corpusEnT, control = list(weighting = weightTfIdf))
tdmEn

tdmEs = TermDocumentMatrix(corpusEsT, control = list(weighting = weightTfIdf))
tdmEs
```

&nbsp;

## 6. Basic text analysis

* TF-IDF word frequencies
* Most relevant words
* Word clouds
```{r}
#TF-IDF word frequencies
freqEn=rowSums(as.matrix(tdmEn))
freqEs=rowSums(as.matrix(tdmEs))
par(mfrow=c(2,1), mar = c(2, 2, 2, 2))
plot(sort(freqEn, decreasing = TRUE),col='blue',main='Word TF-IDF frequencies (English)', xlab='TF-IDF-based rank', ylab = 'TF-IDF')
plot(sort(freqEs, decreasing = TRUE),col='red',main='Word TF-IDF frequencies (Spanish)', xlab='TF-IDF-based rank', ylab = 'TF-IDF')
print('10 most relevant words in English:'); tail(sort(freqEn),n=10)
print('10 most relevant words in Spanish:'); tail(sort(freqEs),n=10)
```

```{r}
#Word Clouds
palEn=brewer.pal(4,'Blues')
palEs=brewer.pal(4,'Reds')
par(mfrow=c(1,1))

unigramTokenizer <- function(x) NGramTokenizer(x, Weka_control(min = 1, max = 1))
tdmEn.unigram = TermDocumentMatrix(corpusEnT,
                                control = list (weighting = weightTfIdf,
                                                tokenize = unigramTokenizer))
tdmEs.unigram = TermDocumentMatrix(corpusEsT,
                                   control = list (weighting = weightTfIdf,
                                                   tokenize = unigramTokenizer))
```

```{r}
# Plot English Wordcloud
freqEn = sort(rowSums(as.matrix(tdmEn.unigram)),decreasing = TRUE)
freqEn.df = data.frame(word=names(freqEn), freq=freqEn)
layout(matrix(c(1, 2), nrow=2), heights=c(1, 10))
par(mar=rep(0, 4))
plot.new()
text(x=0.5, y=0.5, "English wordcloud", cex=1.5,font=2)
wordcloud(freqEn.df$word,freqEn.df$freq,max.words=100,random.order = FALSE, colors=palEn)
```

```{r}
# Plot Spanish Wordcloud
freqEs = sort(rowSums(as.matrix(tdmEs.unigram)),decreasing = TRUE)
freqEs.df = data.frame(word=names(freqEs), freq=freqEs)
layout(matrix(c(1, 2), nrow=2), heights=c(1, 10))
par(mar=rep(0, 4))
plot.new()
text(x=0.5, y=0.5, "Spanish wordcloud", cex=1.5,font=2)
wordcloud(freqEs.df$word,freqEs.df$freq,max.words=100,random.order = FALSE, colors=palEs)
```














