---
title: "NLP Deliverable"
output: html_notebook
---

## Madrid's airbnb reviews, sentiment analysis        
# *Author:* Ana Marin Estañ                        



## 1. Import libraries and data

* Check if all needed packages are installed and libraries added
* Set work directory
* Import data (reviews.csv)


```{r}
packages <- c("rstudioapi", 
              "DT", 
              "tm",
              "ggplot2",
              "googleLanguageR",
              "wordcloud",
              "RWeka",
              "reshape2", 
              "tidyverse", 
              "tidytext", 
              "stringr")

install.packages(setdiff(packages, rownames(installed.packages())))  

library(rstudioapi)
library(DT)
library(tm)
library(ggplot2)
library(googleLanguageR)
library(wordcloud)
library(RWeka)
library(reshape2)
library(tidyverse)
library(tidytext)
library(stringr)
```

```{r}
current_path <- getActiveDocumentContext()$path 
setwd(dirname(current_path))

wdir <- getwd()
cat("Working directory: ", wdir)
```

### Imported data
```{r}
reviews <- read_csv("data/reviews.csv")

datatable(head(reviews, 10))
```


## 2. Load and inspect Corpus 

First, corpus is created form review dataset.

Corpus length is 674987 entries. We're going to work with just the first 1000 entries.

We can also consult the summary and inspect the corpus entries: its content and metadata.

```{r}
corpus = Corpus(VectorSource(reviews$comments))
cat("Original corpus length:", length(corpus), "entries")

corpus = corpus[1:1000]
cat("New corpus lenth:", length(corpus), "entries")

summary(corpus[1:5])
inspect(corpus[[1]])
meta(corpus[[1]])
```


## 3. Create and transform TDM 

In this section a Term-Document matrix is created with the following transformations:

* Text set to lower case
* Strip white spaces
* Remove English stopwords
* Remove punctuarions
* Remove numbers
* Stemming
* TF_IDF weighting
* Remove empty documents



```{r}
tdm = TermDocumentMatrix(corpus,
                         control = list(tolower = TRUE,
                                        stopwords = TRUE,
                                        removePunctuation = TRUE, 
                                        removeNumbers = TRUE,
                                        stemming = TRUE,
                                        stripWhitespace = TRUE,
                                        weighting = weightTfIdf)
                         )

colTotals <- apply(tdm, 2, sum) 
tdm <- tdm[ , colTotals> 0]
tdm
inspect(tdm[2500:2510,1:10])
```

```{r}

```

